A Horrocks-type theorem for even orthogonal $K_2$

### 2020-08-10 horrocks.tex
Fix misprint

\begin{document}
%%%%% ------------- fill in your data below this line  -------------------
%%%%%    The following lines \Title ... \EndAddress must ALL be present
%%%%%    and in the given order.
\Title
A Horrocks-Type Theorem for Even Orthogonal $\mathrm{K}_2$
\ShortTitle 
A Horrocks-Type Theorem for $\mathrm{KO}_2$ 
\SubTitle   
%%%%%    A possible subtitle goes here.
\Author 
Andrei Lavrenov and Sergey Sinchuk
\ShortAuthor 
A. Lavrenov, S. Sinchuk
\EndTitle
\Abstract 
We prove the Horrocks theorem for unstable even-dimensional orthogonal Steinberg groups. The Horrocks theorem for Steinberg groups is one of the principal ingredients needed for the proof of the $\K_2$-analogue of Serre’s problem,  whose positive solution is currently known only in the linear case.
\EndAbstract
\MSC 
19C20
\EndMSC
\KEY 
Steinberg group, $\mathrm{K}_2$-functor, Quillen--Suslin theorem, Horrocks theorem, $\mathbb{P}^1$--glueing
\EndKEY
%%%%%    All 4 \Address lines below must be present. To center the last
%%%%%    entry, no empty lines must be between the following \Address
%%%%%    and \EndAddress lines.
\Address
Andrei Lavrenov
Chebyshev Laboratory 
St. Petersburg State University 
14th. Line V.O. 29b
199178, St. Petersburg
Russia
avlavrenov@gmail.com
\Address
Sergey Sinchuk
Chebyshev Laboratory 
St. Petersburg State University 
14th. Line V.O. 29b
199178, St. Petersburg
Russia
sinchukss@gmail.com
\Address
\Address
\EndAddress
%%
%%       Make sure the last tex command in your manuscript
%%       before the first \end{document} is the command  \Addresses
%%
%%---------------------Here the prologue ends---------------------------------
%%--------------------Here the manuscript starts------------------------------

>>>>

\begin{document}
%%%%% ------------- fill in your data below this line  -------------------
%%%%%    The following lines \Title ... \EndAddress must ALL be present
%%%%%    and in the given order.
\Title
A Horrocks-Type Theorem for Even Orthogonal $\mathrm{K}_2$
\ShortTitle 
A Horrocks-Type Theorem for $\mathrm{KO}_2$ 
\SubTitle   
%%%%%    A possible subtitle goes here.
\Author 
Andrei Lavrenov and Sergey Sinchuk
\ShortAuthor 
A. Lavrenov, S. Sinchuk
\EndTitle
\Abstract 
We prove the Horrocks theorem for unstable even-dimensional orthogonal Steinberg groups. The Horrocks theorem for Steinberg groups is one of the principal ingredients needed for the proof of the $\K_2$-analogue of Serre's problem,  whose positive solution is currently known only in the linear case.
\EndAbstract
\MSC 
19C20
\EndMSC
\KEY 
Steinberg group, $\mathrm{K}_2$-functor, Quillen--Suslin theorem, Horrocks theorem, $\mathbb{P}^1$--glueing
\EndKEY
%%%%%    All 4 \Address lines below must be present. To center the last
%%%%%    entry, no empty lines must be between the following \Address
%%%%%    and \EndAddress lines.
\Address
Andrei Lavrenov
Chebyshev Laboratory 
St. Petersburg State University 
14th. Line V.O. 29b
199178, St. Petersburg
Russia
avlavrenov@gmail.com
\Address
Sergey Sinchuk
Chebyshev Laboratory 
St. Petersburg State University 
14th. Line V.O. 29b
199178, St. Petersburg
Russia
sinchukss@gmail.com
\Address
\Address
\EndAddress
%%
%%       Make sure the last tex command in your manuscript
%%       before the first \end{document} is the command  \Addresses
%%
%%---------------------Here the prologue ends---------------------------------
%%--------------------Here the manuscript starts------------------------------
